---
title: "Untitled"
author: "Teresa Domaszewska"
date: "May 2, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project report

To perform given tasks, I downloaded the training and test data sets as .csv files and read them into R. The data set describes measurements from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. I excluded the columns with missing data in the training data set and visualized it's content, plotting the relationship of every variable and the variable  "classe", eg:

```{r plot1}
library(caret)
testing <- read.csv("pml-testing.csv", header = TRUE)
training <- read.csv("pml-training.csv", header = TRUE)

training <- training [, -1]
testing <- testing [, -1]

training <- training [, colSums(is.na(training))<nrow(training)]
training <- training [, colSums(is.na(training))==0]
training <- training [, -c(11:19, 42:47, 51:59, 73:81)]
testing <- testing [, colSums(is.na(testing))<nrow(testing)]
testing <- testing [, colSums(is.na(testing))==0]

plot(training$classe, training$roll_belt)
plot(training$classe, training$total_accel_belt)
```

Some of the predictors presented bigger and some no influence on the predicted variable. Some of them could also be correlated. I decided to use all the predictors and random forest method without preprocessing to build the model with proximity measures calculated.

```{r model}
modFit <- train(classe~., data=training, method = "rf", prox = TRUE)
pred <- predict(modFit, testing)
```

Cross validation has been performed as random sampling with replacement (bootstrapping) within the training data set. Reasampling results across tuning parameters:

```{r error}
modFit$results
```

The out of sample error will be larger than 0,01% (which is in-sample error).

I decided to use random forest method including all predictors for which the data is available to include all available information in the model building.

